An Extensible Approach to Verification of Embedded Systems

### 2014-05-01 tech-project/implementation.tex
more progress

The previous iteration of this tool \cite{regula:2010} (favoring static allocation) carries out ``pseudo allocation"  by effectively introducing second pass to the compiler dedicated to replacing all formal parameters, with their corresponding facility-instantiated literal values. This additional, hidden step to compilation is less than ideal in the context of a verifying compiler designed from the ground up to be a single pass system. We feel the work we present here avoids these wrinkles with a dynamic approach.

>>>>

The previous iteration of this tool \cite{regula:2010} achieves static allocation by effectively introducing a second pass to the compiler dedicated to replacing all formal parameters with their corresponding facility-instantiated literal values. This additional, hidden step to compilation is less than ideal in the context of a verifying compiler designed from the ground up to be a single pass system. We feel the work we present here avoids these wrinkles with a dynamic approach.

### 2014-05-01 tech-project/led_trans.tex
more progress

void LED_Telos_Demo_destroy() {
    free_Std_LED_Realiz_for_LED_Template(
    				    LED_Fac_Var.core);
    Std_Bool_Fac_destroy();
    Std_Int_Fac_destroy();
} ...
\end{verbatim}
\end{minipage}
\caption{C Translation of \texttt{LED\_Telos\_Demo}.}
\label{fig:demo}
\end{figure*}

@@

Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right). The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{Leds\_Fac}. One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept. Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion.

@@

Clearly facilities and other modules highly reliant on facility instantiations are no doubt going to consume much more memory than the small example detailed here. To help alleviate some of th

@@

\begin{figure}
\begin{verbatim}
int Main() {
  while(TRUE) {
    Toggle(L, 0);
    Wait_500_Milli_Seconds();
    Toggle(L, 1);
    Wait_500_Milli_Seconds();
    Toggle(L, 2);
    Wait_500_Milli_Seconds();
  }
}

int main() {
  LED_Telos_Demo_create();
  Main();
  LED_Telos_Demo_destroy();
}
\end{verbatim}
\label{fig:loop}
\end{figure}
%
%
%
%
%
%
%
%
%
%
%
%
%
%

>>>>

void LED_Telos_Demo_destroy() {
    free_Std_LED_Realiz_for_LED_Template(
    				    LED_Fac_Var.core);
    Std_Bool_Fac_destroy();
    Std_Int_Fac_destroy();
} ...
\end{verbatim}
\end{minipage}
\caption{C Translation of \texttt{LED\_Telos\_Demo}. The .h (left) and .c implementation (right).}
\label{fig:demo}
\end{figure*}

@@

Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right). The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{Leds\_Fac}. One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept. Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion (as illustrated after the assignment of \texttt{Toggling\_Capability}).

@@

Clearly, facilities and other modules highly reliant on instantiated facilities are no doubt going to consume much more memory than the small example detailed here -- as each would (naively) be represented as a struct. To help alleviate some of this memory usage, we make special considerations in the translated code to only create structs for \textit{enhanced} facilities. That is, \textit{unenhanced} facilities (comprising structs with only a single \texttt{core} field) are not created, but rather, dereferenced manually within the source.

The body of the .c file (omitted from Figure \ref{fig:demo} for clarity and space), operates as expected: A C while loop iterates indefinitely, making successive 500ms delayed calls to toggle each LED. Perhaps the last thing worth mentioning is the invoking main method:

\begin{verbatim}
int main() {
    LED_Telos_Demo_create();
    Main();
    LED_Telos_Demo_destroy();
}
\end{verbatim}

@@

%\begin{figure}
%\begin{verbatim}
%int Main() {
%  while(TRUE) {
%    Toggle(L, 0);
%    Wait_500_Milli_Seconds();
%    Toggle(L, 1);
%    Wait_500_Milli_Seconds();
%    Toggle(L, 2);
%    Wait_500_Milli_Seconds();
%  }
%}

%int main() {
%  LED_Telos_Demo_create();
%  Main();
%  LED_Telos_Demo_destroy();
%}
%\end{verbatim}
%\label{fig:loop}
%\end{figure}

### 2014-05-01 tech-project/related_works_and_conclusion.tex
more progress

There are a number of existing systems that ultimately seek to prove the functional correctness of programs. While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion. Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}. Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches to verification. Substituting RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code. Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.

Another system, also a Microsoft research endeavor, is VCC -- a system designed for the verification of C programs \cite{vcc:2009}. One of the main draws of VCC is that it has mechanisms for verification of concurrent code -- an ideal feature when presented with asynchronous, event driven code common in most embedded applications.

RESOLVE differs from the projects mentioned above most notably in that it does not make use of third party automated provers or decision procedures to discharge verification conditions. Rather, it makes use of an integrated, minimalist term rewrite prover that applies higher order theorems and definitions in attempting to transform givens into a provable goal.

@@

Using embedded application development as an example, we perceive this work as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts. Indeed, the realm of embedded systems provides an ideal stepping off point for this challenge, as it encourages (and indeed, requires) RESOLVE to provide support for not only new target languages (namely C), but also new language constructs that give the user the ability to author drivers required for any serious embedded application. While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here.

>>>>

Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that 
%There are a number of existing systems that ultimately seek to prove the functional correctness of programs. While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion. Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}. Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches to verification. Substituting RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code. Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.

%Another system, also a Microsoft research endeavor, is VCC -- a system designed for the verification of C programs \cite{vcc:2009}. One of the main draws of VCC is that it has mechanisms for verification of concurrent code -- an ideal feature when presented with asynchronous, event driven code common in most embedded applications.

%RESOLVE differs from the projects mentioned above most notably in that it does not make use of third party automated provers or decision procedures to discharge verification conditions. Rather, it makes use of an integrated, minimalist term rewrite prover that applies higher order theorems and definitions in attempting to transform givens into a provable goal.

@@

Using embedded application development as an example, we perceive this work as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts. Indeed, the realm of embedded systems provides an ideal stepping off point for this challenge, as it encourages (and indeed, requires) RESOLVE to provide support for not only new target languages (namely C), but also new language constructs that give the user the ability to author drivers required for any serious embedded application. While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here. Indeed, by being able to prove aspects of this system at this level of granularity (down to time and space) confidence in the systems we rely upon everyday (embedded systems included)

proving memory and time constraints on any allocation scheme will provide assurance that we never exceed limitations or behave unexpectedly.

Moreover, if we do In the future if we do it dynamically or statically there is no difference, if the static people are concerned about memory, the It might not seem like we're doing much w
